### 2015-05-29 ISWAG_PRESENTATION/PRESENTATION_ISWAG.TEX
iswag presentation

\fancyhead[L]{\theslideheading}
\fancyhead[R]{\textcolor{blue}{\eadsccr \thepage }}
\fancyfoot[R]{\textcolor{blue}{}}
\fancyfoot[L]{\textcolor{blue}{Bordeaux, le \today }}
\renewcommand\headwidth{\textwidth}
\autoslidemarginstrue

@@

\renewcommand\makeslideheading[1]{\par
   \fcolorbox{black}{Pink}{\color{yellow}\theslidesection. #1}\par
}
\renewcommand\makeslidesubheading[1]{\par
   \leavevmode\hspace*{1cm}%
   \textcolor{Mygreen}{\alph{slidesubsection}. #1}\par
}

@@

\slideframe{none}

%\XgrDefinitFormat{*}{line=0,mark=0,ll=1}
%\XgrDefinitFormat{pr}{}
%\XgrDefinitFormat{ks}{line=-1,mark=8,ll=0.4}

\begin{document}
\slidepagestyle{fancy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{slide}
%\begin{figure}[ht]\begin{center}\includegraphics[height=3cm]{logo.eps}\end{center}\end{figure}
\begin{center}
\textcolor{blue}{\large Optimisation du maillage interne}\\
\vspace{0.25 cm}
%\eadsccr
\end{center}
\end{slide}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\small{
\begin{slide}
Soit $N\in\mathbb{N}$ le nombre de noeuds de notre maillage.
\newline
%Soit $\left(X_i\right)_{i \in \left{1,N\right}}$ les sommets de notre graphe orienté.
Soit $\left(X_i\right)_{i \in \left\{1,...,N\right\}}$ les sommets de notre graphe orienté.
\newline
Soit $\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$ la matrice adjacente de notre graphe orienté.
\begin{equation}
\max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} trafic\left(X_i\right)\times pageRank(X_i)\right\}
\end{equation} 
\end{slide}
\begin{slide}
Soit $N\in\mathbb{N}$ le nombre de noeuds de notre maillage.
\newline
Initialisation du page rank :
\begin{equation}
\forall u \ PR\left(u\right)=\frac{1}{N}
\end{equation} 
Calcul itératif :
\begin{equation}
PR\left(u\right)= \frac{\left(1-c\right)}{N} + c \times \sum_{v \rightarrow u}\frac{PR\left(v\right)}{card\left(\left\{v\rightarrow u\right\}\right)}
\end{equation}
\end{slide}
\end{document}

>>>>

\fancyhead[L]{\theslideheading}
\fancyhead[R]{\textcolor{blue}{\eadsccr \thepage }}
\fancyfoot[R]{\textcolor{blue}{}}
\fancyfoot[L]{\textcolor{blue}{Deauville, 03 June 2015 }}
\renewcommand\headwidth{\textwidth}
\autoslidemarginstrue

@@

\renewcommand\makeslideheading[1]{\par
   \fcolorbox{black}{Mygreen}{\color{yellow}\theslidesection. #1}\par
}
\renewcommand\makeslidesubheading[1]{\par
   \leavevmode\hspace*{1cm}%
   \textcolor{Mygreen}{\alph{slidesubsection}. #1}\par
}

@@

\slideframe{none}
%\XgrDefinitFormat{*}{line=0,mark=0,ll=1}
%\XgrDefinitFormat{pr}{}
%\XgrDefinitFormat{ks}{line=-1,mark=8,ll=0.4}
\begin{document}
\slidepagestyle{fancy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{slide}
\thispagestyle{plain}
\begin{center}
\textcolor{blue}{\huge Internal mesh optimization}\\
\textcolor{blue}{\huge Semantic linking and siloing}\\
\textcolor{blue}{\huge Big data}\\
\vspace{0.25 cm}
\textbf{DUPREY Stéfan}\\
\small{\textbf{Cdiscount}\\

}
%\eadsccr
\end{center}
\end{slide}

@@

{\small{
\begin{slide}
\slidecontents
\renewcommand\theslideheading{Plan}
\end{slide}
\begin{slide}
\slideheading{Introduction}
\textbf{\textcolor{blue}{\large Objective : give you an overview of the meshing optimization done at Cdiscount, the first french e-commerce web site }}
\small{
\newline $\bullet$ Heuristic based optimization algorithm to push specific products 
\newline $\bullet$ An e-commerce pitch
\newline $\bullet$ Semantic similarity and constraining for shrinking our universe
\newline $\bullet$ Big data implementation
}
\end{slide}
\begin{slide}
\slideheading{Some notations}
Let $N\in\mathbb{N}$ be the number of nodes in our mesh.
\newline
Let $\left(X_i\right)_{i \in \left\{1,...,N\right\}}$ be the vertices (URLs) of our oriented graph.
\newline
Let $\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$ be the adjacency matrix of our oriented graph.
\newline
Let here define f, a given data per URL, which gives a potentiality metrics for our vertices.
\begin{equation}
\begin{array}{ccccc}
f & : & \left(X_i\right)_{i \in \left\{1,...,N\right\}} & \to & \mathbb{R}^{+} \\
& & x & \mapsto & f(x) \\
\end{array}
\end{equation}
\end{slide}
\begin{slide}
\slideheading{In-rank computation}
We restrain the universe to our site where we compute the standard page-rank.
\newline
Initialization :
\begin{equation}
\forall u \ PR\left(u\right)=\frac{1}{N}
\end{equation} 
Iterative computation :
\begin{equation}
PR\left(u\right)= \frac{\left(1-c\right)}{N} + c \times \sum_{v \rightarrow u}\frac{PR\left(v\right)}{card\left(\left\{v\rightarrow u\right\}\right)}
\end{equation}
\end{slide}
\begin{slide}
\slideheading{Exhaustive brute force doesn't work}
For a $N=10^6$ millions URLs web site, we have $2^{N^{2}}$ with a 2048 bits mantissa, 256 bits exponent 
\newline
\scriptsize{
$2^{{10^6}^2}=$
\\ \newline 9.5762442314927432848050594956989483747127095675192905698213128517073583274396016675898
\\ \newline 714705184143146468453752442806484690561169975498415015777492655947375270159476651418975
\\ \newline 300707658547568802353384879419803574730952480197774380552040662758127609571333683703207
\\ \newline 910070247048194459504686986124786492353387550318495241621572271925127288273993787778380
\\ \newline 450774809611395810191417363401889038757182279484019203870177413318113073911418463615759
\\ \newline 647977538478560166958988721048687854280187283661925937530017243461145905573802314471888
\\ \newline 491758757162677684017424597014433418179115289463552630751896559312213624470617453325056
\\ \newline 5836008e+301029995663
}
\end{slide}
\begin{slide}
\slideheading{Picturing our smallest store : jewelery }
\begin{center}
\epsfig{file=page_rank.eps,height=6.5cm,width=8.cm}
\end{center}
\end{slide}
\begin{slide}
\slideheading{Heuristic based algorithm}
We want here to optimize the adequation of our mesh $\left(X_i\right)$ to our potentiality vector $f$.
\begin{equation}
\max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} trafic\left(X_i\right)\times pageRank(X_i)\right\}
\end{equation} 
\end{slide}
\begin{slide}
\slideheading{Genetic algorithm}
\textbf{\textcolor{blue}{\large What a genetic algorithm }}
\small{
\newline $\bullet$ Genetic algorithm mimics evolutionary biology to find approximate solutions to optimization problems 
\newline $\bullet$ Start with an initial generation of candidate solutions that are tested against the objecive function (fitness of the individual)
\newline $\bullet$ Subsequent generations evolve from the first through selection, crossover and mutation
\newline $\bullet$ The individual that best minimizes the given objective is returned as the ideal solution
}
\newline \textbf{\textcolor{blue}{\large Why a genetic algorithm }}
\small{
\newline $\bullet$ Lots of local minima to avoid
\newline $\bullet$ Non continuous universe, constraints and objective
\newline $\bullet$ Problem with noise and non-smooth data
}
\end{slide}
\end{document}
